---
title: "FY21 Search 1 Planning: Historical Analysis of Lead Purchases October 2017 - April 2020"
author: "Office of Marketing and Brand Management"
date: "September 11, 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r}
library(knitr)
library(tidyverse)
```


```{r}
# library(salesforcer)
# library(knitr)
# library(RForcecom)
# username <- "christine.iyer@maine.edu"
# password <- "1Edithandoliver"
# securityToken <- "iFhpXgaXnuP3L5PQr69Zw2yOy"
# instanceURL <- "https://login.salesforce.com/"
# apiVersion <- "44.0"

#auth <- sf_auth(username = username, password = password, security_token = securityToken,
#login_url = getOption("https://login.salesforce.com/"))



# session <- sf_auth(username, password, securityToken, instanceURL, apiVersion)
# username <- "christine.iyer@maine.edu"
# password <- "1EdithandoliveriFhpXgaXnuP3L5PQr69Zw2yOy"
# #securityToken <- ""
# instanceURL <- "https://na24.salesforce.com/"
# apiVersion <- "44.0"
# 
# 



#session <- rforcecom.login(username, password, instanceURL,apiVersion  ) 

# my_soql <- sprintf("SELECT Id,
#                            CreatedDate,
#                            Email, 
#                            FirstName, 
#                            LastName,
#                            TargetX_SRMb__Status__c, TargetX_SRMb__Student_Type__c,
#                            TargetX_SRMb__Anticipated_Start_Term__c,
#                            TargetX_SRMb__Anticipated_Start_Term_Year__c, 
#                            TargetX_SRMb__Anticipated_Start_Year__c,
#                            App_Application_Date__c,  
#                            TargetX_SRMb__Gender__c,  
#                            TargetX_SRMb__Last_Data_Input_Source__c,                                                                Initial_Source_Date__c, 
#                            Initial_Referral_Source__c, 
#                            Recruiting_Category__c,
#                            Ref__c, 
#                            Primary_State_Code__c
#                            
#                     FROM Contact 
#                     WHERE TargetX_SRMb__Status__c != 'Lead' 
#                     AND Recruiting_Category__c != ' '")
# 
# queried_records <- sf_query(my_soql)
```


## Brief Description

As requested, I have compiled a historical and updated report of all of the leads and their conversions through the application funnel based on search name purchases between October, 2017 and April, 2020. 

```{r load data}
data <- read.csv("C:/Users/christine.iyer/Box/FY21_Search/FY21_SR_Search_1_Planning_Historical_Analysis/Data/RawDataAllSearch.csv", header = T, stringsAsFactors = F)
```

```{r fix dates}

```



```{r pressure, echo=FALSE}

dateColumns <- c("Birthdate", "Initial.Source.Date", "Created.Date",                 "Last.Modified.Date", "App.Application.Date", "App.Admit.Date", "App.Deposit.Date" )

Data <- data %>% 
  mutate_at(
    vars("Birthdate", "Initial.Source.Date", "Created.Date",                 "Last.Modified.Date", "App.Application.Date", "App.Admit.Date", "App.Deposit.Date"), 
    as.POSIXct,
    format = "%m/%d/%Y"
    )
Data <- Data %>% 
  mutate(State = ifelse(Primary.State.Province == "Maine", "In-State", "Out-State")) %>% 
  group_by(Created.Date, Anticipated.Start.Year, Recruiting.Category, State, Student.Stage, App.Application.Status, Lead.Segment.NRCCUA, Lead.Segment.Cappex, Lead.Segment.College.Board) %>% summarise(n = n())
write.csv(Data, "C:/Users/christine.iyer/Box/FY21_Search/FY21_SR_Search_1_Planning_Historical_Analysis/Data/RawDataAllSearch_Tidied_Step_1.csv",row.names = F)
```

## Findings

```{r}
newData <- read.csv("C:/Users/christine.iyer/Box/FY21_Search/FY21_SR_Search_1_Planning_Historical_Analysis/Data/RawDataAllSearch_Tidied_Step_2.csv", header = T, stringsAsFactors = F)
SRData <- newData %>% 
  filter(Class == "SR") %>% 
  group_by(Created.Date,Vendor, Class) %>% 
  summarise(Leads = sum(Lead), 
            Inquiry = sum(Inquiry), 
            Applied = sum(Applied), 
            Admitted = sum(Admitted), 
            Confirmed = sum(Confirmed), 
            Enrolled = sum(Enrolled))
JRData <- newData %>% 
  filter(Class == "JR") %>% 
  group_by(Created.Date,Vendor, Class) %>% 
  summarise(Leads = sum(Lead), 
            Inquiry = sum(Inquiry), 
            Applied = sum(Applied), 
            Admitted = sum(Admitted), 
            Confirmed = sum(Confirmed), 
            Enrolled = sum(Enrolled))
bothData <- rbind.data.frame(SRData, JRData)
# write.csv(bothData, "C:/Users/christine.iyer/Box/FY21_Search/FY21_SR_Search_1_Planning_Historical_Analysis/Data/RawDataAllSearch_Tidied_Step_3.csv", row.names = F)
```

### Senior Lead Performance

```{r}
newestData <- read.csv("C:/Users/christine.iyer/Box/FY21_Search/FY21_SR_Search_1_Planning_Historical_Analysis/Data/RawDataAllSearch_Tidied_Step_3.csv", header = T, stringsAsFactors = F)
newestData <- newestData %>% 
  mutate(InqYield = paste0(round(Inquiry/Leads*100,2), "%"), 
         AppYield = paste0(round(Applied/Leads*100, 2), "%"), 
         #EnrollYield = paste0(round(Enrolled/Leads*100),2, "%"), 
         Vendor = ifelse(Vendor == "College Board", "CB", 
                         ifelse(Vendor == "NRCCUA", "NC", "Both")), 
         Leads = prettyNum(Leads, big.mark = ","),
         Inquiry = prettyNum(Inquiry, big.mark = ","), 
         Applied = prettyNum(Applied, big.mark = ","),) 

newestData[newestData == 0] <- "~"

kable(newestData %>% filter(Class == "SR")
      )


```

### Junior Lead Performance

```{r}
kable(newestData %>% 
        filter(Class == "JR"))
```

## Conclusions

* FY20 Senior search names don't have data beyond application; however, the inquiry and application data was updated 9/11/20. FY20 Junior search names reflect their current status. The most recent campaign concluded on June 25, 2020. 


#

\href{https://www.wrike.com/open.htm?id=562875559}{{\color{blue}{\underline{Wrike Project Details}}}}

\href{https://github.com/edithbird/FY21-senior-search-1-planning-historical-analysis}{{\color{blue}{\underline{Github Repository}}}}